---
title: "Lab2_DataSciteam"
author: "Breanna, Poramate, Emma, Juanca, Jack"
date: "9/4/2019"
output: html_document
------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Team name: 
# The main goal: 

# About me: Poramate Nakkirt (Pao)
```{r}
library(knitr)
include_graphics("pao.ipg")
```
# Question:  What specifically could I have the most chance to win the lottery in Colorado? 
# Fortunately, I have a gap of 6 months after my graduation. I am planning to travel in many countires like South Americas and Europe. I am very excited to do so. This may be my first time going outside the US. If possible in the next five years, I like to do more. 
# My greatest carreer accomplishment will be the interdisciplinary professional on Data Science, Statistics, and Mathematics with receiving a high salary. 
# This class is a great learning on the very popular material. I hope to learn a skill of R programming effectively and also basic skill of statistical concept. Another thing is to have an opportunity to solve a real-world problems using Data Science knowledge.
# Something personal, I like Colorado becasue it is great for outdoor sports like hiking or skiing. Be socialized and do whatever fun. 
# Feedback for Pao:

Part One: Individual About Me

```{r}
include_graphics("IMG_6878")
```
# About Me: Emma Sweeden

#My name is Emma Sweeden, I am a sophomore in Applied Mathematics hoping to focus in Data Science and Computer Science.

#I wonder how successful my major will be directly out of college. The answer to this could be found by analyzing data.

#I would love to have a nice paying job six months after college that I gain lots of experiene from.  After five years out of college, I would like to be managing people or a team working on computer science related projects. 

#I want to make a difference for women across the globe, so if I could do that somehow through my career, that would be a major success.

#I am hoping to add another coding language to the catalog I am currently building for myself and use my experience in R to help myself getting an internship or future job.  

#Another random of interest of mine is sports.  I would love to be able to use my knowledge of data science to perhaps report statistics for the NFL.  That's truly a "dream job."

#Part Two: Feedback
