---
title: "Lab2_DataSciteam"
author: "Breanna, Poramate, Emma, Juanca, Jack"
date: "9/4/2019"
output: html_document
------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Team name: 
# The main goal: 

# About me: Poramate Nakkirt (Pao)
```{r}
library(knitr)
include_graphics("pao.ipg")
```
# Question:  
# Fortunately, I have a gap of 6 months after my graduation. I am planning to travel in many countires like South Americas and Europe. I am very excited to do so. This may be my first time going outside the US. If possible in the next five years, I like to do more. 
# My greatest carreer accomplishment will be the interdisciplinary professional on Data Science, Statistics, and Mathematics with receiving a high salary. 
# This class is a great learning on the very popular material. I hope to learn a skill of R programming effectively and also basic skill of statistical concept. Another thing is to have an opportunity to solve a real-world problems using Data Science knowledge.
# Something personal, I like Colorado becasue it is great for outdoor sports like hiking or skiing. Be socialized and do whatever fun. 
# Feedback for Pao:

