---
title: "Lab3"
authors:  "Breanna, Poramate, Emma, Juanca, Jack"
date: "09/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

**Overall Question**

**Why the qestion is important**

**Team's plot**

**Answer to the question**

**Recommendation**

**Individual plots and findings**

```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = weight, fill = genhlth), position = "fill")
```

**Findings**

* The ratio of people with poor health to the people with good or better health drastically increases in people above 300 pounds
* There are less people with good health or better who weigh under 100 pounds
* The ratio of people with poor or fair health to the people with good or better health is much lower in people who weigh between 100 and 250 pounds.

**Who did what**
*Breanna: I created a plot that showed weight and health are related. The data showed that people who were between 100 and 250 pounds tended to be healthier than those below or above. I used the bar geom and adjusted the fill of the data. I used the position adjustment to compare the proportions of people's health based off of their weight.