---
title: "Lab 4"
authors: "Breanna, Poramate, Emma, Juanca, Jack"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care
```

### Overall Questions
1. Does the data provide evidence supporting the Surgeon General's assertion that mothers who smoke have increased rates of premature delivery(before 270 days)?

2. Does the data provide evidence supporting the Surgeon General's assertion that the newborns of mothers who smoke have smaller birth weights at every gestational age(number of days into pregnancy when child is born)?

### Team's Plots and Answers

**Question #1 Plot**

```{r}
ggplot(data = babies) +
  geom_jitter(mapping = aes(x = smoke, y = Premature))
```

**Question #1 Answer:**

The data shows that mothers who smoke have slightly increased rates of premature delivery, therefore supporting the Surgeon Generals assertion. 

### Team's Recommendation

### Team's Plots and Answers to "Preliminary" Question

**Preliminary Question**

* Which variables are similar between smokers and nonsmokers? Which are different?

**Plots**

**Answers**

### Individual Findings and Plots

**Breanna**

```{r, echo = FALSE, warning = FALSE}
ggplot(data = babies) +
  geom_jitter(mapping = aes(x = Premature, y = med, color = smoke)) +
  facet_wrap(~mrace)
```

Findings:

* The amount of mothers who smoke during the pregnancy is greater in white and black mothers.
* The babies that are born premature have a majority of mothers who smoked while pregnant.
* The majority of mothers who smoked had lower educations.

### Who did what

* Breanna: I created a jitter plot showing the relationship between babies who were born premature and the mothers education. I used the facet_wrap() function to show how the data differed around the mothers race. The data showed that the mothers who smoked while pregnant were mostly less educated and white or black. I used the jitter function and adjusted the color to show what babies had mothers who smoked while pregnant. 